Top-down and bottom-up cohesiveness\\in microbial community coalescence

### 2021-06-03 draft/draft_v4.tex
typo

\begin{figure}[!h]
\centering
\internallinenumbers
\includegraphics[scale=0.9,keepaspectratio]{figs/figS4.pdf}
\caption{\textbf{Top-down co-selection is robust in the MicroCRM.}
We ran simulations of community coalescence following the same
procedure described in the main text, but randomly sampling the
following prameters of the MicroCRM
uniformly within the indicated ranges:
number of species per community sampled at initialization ($S$) between 10 and 90;
total number of species families between 1 and 5;
total number of species per family ($S_A$) between 400 and 1200;
total number of generalist species ($S_{gen}$) between 100 and 380;
specialist species preference strength ($q$) between 0.5 and 1;
number of resource classes between 1 and 5;
number of resources per class ($M_A$) between 3 and 17;
leakage fraction ($l_{\alpha}$) between 0.45 and 0.95;
maintenance cost ($m_i$) between 0 and 0.2;
standard deviation of the sum of consumption rates ($\sigma_c$) between 2 and 4;
sparsity of the metabolic matrix between 0.05 and 0.95;
fraction of secretion flux to resources of the same type ($f_s$) or to waste resources ($f_w$) between 0.05 and 0.45.
The metabolic matrix was randomly chosen to be such that $D_{i\beta\alpha}=D_{j\beta\alpha}$ or such that
$D_{i\beta\alpha} \neq D_{j\beta\alpha}$ for all species ($i$, $j$) and resources ($\alpha$, $\beta$).
Both options were given equal probabilities.
For each randomly sampled set of parameters, we ran 100 simulations
and quantified the ability of the pairwise competition
of dominants to predict coalescence outcomes (see \figref[a]{fig2}), i.e. the strength of top-down co-selection
in each regime.
The histogram shows that top-down co-selection is robust throughout the parameter space in the MicroCRM.}
\label{figSX}
\end{figure}

>>>>

\begin{figure}[!h]
\centering
\internallinenumbers
\includegraphics[scale=0.9,keepaspectratio]{figs/figS4.pdf}
\caption{\textbf{Top-down co-selection is robust in the MicroCRM.}
We ran simulations of community coalescence following the same
procedure described in the main text, but randomly sampling the
following prameters of the MicroCRM
uniformly within the indicated ranges:
number of species per community sampled at initialization ($S$) between 10 and 90;
total number of species families between 1 and 5;
total number of species per family ($S_A$) between 400 and 1200;
total number of generalist species ($S_{gen}$) between 100 and 380;
specialist species preference strength ($q$) between 0.5 and 1;
number of resource classes between 2 and 5;
number of resources per class ($M_A$) between 3 and 17;
leakage fraction ($l_{\alpha}$) between 0.45 and 0.95;
maintenance cost ($m_i$) between 0 and 0.2;
standard deviation of the sum of consumption rates ($\sigma_c$) between 2 and 4;
sparsity of the metabolic matrix between 0.05 and 0.95;
fraction of secretion flux to resources of the same type ($f_s$) or to waste resources ($f_w$) between 0.05 and 0.45.
The metabolic matrix was randomly chosen to be such that $D_{i\beta\alpha}=D_{j\beta\alpha}$ or such that
$D_{i\beta\alpha} \neq D_{j\beta\alpha}$ for all species ($i$, $j$) and resources ($\alpha$, $\beta$).
Both options were given equal probabilities.
For each randomly sampled set of parameters, we ran 100 simulations
and quantified the ability of the pairwise competition
of dominants to predict coalescence outcomes (see \figref[a]{fig2}), i.e. the strength of top-down co-selection
in each regime.
The histogram shows that top-down co-selection is robust throughout the parameter space in the MicroCRM.}
\label{figSX}
\end{figure}
